---
title: "owner_TylerKruzan"
author: "Tyler Kruzan"
date: "9/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Lab 1

R Markdown
Tyler Kruzan

####I am studying Data Analytics

####Tools for Organizing Work:
1. Follow a uniform structure for taking notes & saving files.
2. Organize documents and files by Class and semester taken. 
3. Pay attention in class!

####Interesting Fact: I play tennis


##Understanding Concepts:
1. Explain the difference between Git and Github.
  Git is a version control system that helps programmers track different drafts of code. 
  Github is a remote repository that allows programmers to save drafts on the web and collaborate with others
  
2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 
  Yes, you can use Git without Github, but in order to use Github you must use git and bash commands.
  We don't use them independently so that we can easily track and collaborate on our files. 
  

3. What is a repository in Git and how can you create a repository in Git (write out the command(s))?



# Coding Exercises 

  You may work on this with your partner or individually. 

1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.

numNas = length(which(is.na(X)))
which(is.na(X) & is.na(Y))


2. Run the following code: 

   ```{r}
   age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   ```
   
  This code took three vectors (`age`, `smoker`, and `weight`) and binded them together into an `R` object known as a 
  `data.frame`. The advantage of `data.frame` is that it can handle vectors of different types. For example, age is a numeric 
    vector but smoker status is a character vector (T or F). We named this `data.frame` as `example_data`. I obviously made a
    data entry error: someone cannot have 0 weight. The correct weight should be 150 pounds. Write one line of code that can 
    easily correct this using the `[]` syntax. 
example_data[3,3] = 150

3. In the following I have two code snippets. Turn these code snippets into functions. Think about what each function does
  and what you would name it. How many arguments does it need? 
  ```{r, eval=FALSE}
  mean(is.na(x)) #finds the mean of a certain value

  x / sum(x, na.rm = TRUE) #finds the mean of certain vector with NA values removed
  ```
  
  
4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors. 


both_na = function(x,y) {
  length(which(is.na(x) & is.na(y)))
}